---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# hyperr8

<!-- badges: start -->
<!-- badges: end -->

The goal of hyperr8 is to properly handle datasets that have a rate versus a time.

## Installation

You can install the development version of hyperr8 from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("bomeara/hyperr8")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(hyperr8)
car_rates <- generate_car_simulation()
head(car_rates)
```

This generates a dataset with 1,000 cars with an average speed of 70 mph and an average driving time of 3 hours, so an average distance traveled of 210 miles. The driving time and distance traveled are highly correlated (0.99). Just looking at the raw distance versus time, we see a strong correlation:

```{r, echo=FALSE}
plot(car_rates$time, car_rates$distance, pch=20, col=rgb(0,0,0,0.2), xlab="Time", ylab="Distance")
```

But if we plot the estimated rate versus time, we see a hyperbola:

```{r, echo=FALSE}
plot(car_rates$time, car_rates$rate, pch=20, col=rgb(0,0,0,0.2), xlab="Time", ylab="Rate")
```

And this is even more clear on a log-log plot:

```{r, echo=FALSE}
plot(car_rates$time, car_rates$rate, pch=20, col=rgb(0,0,0,0.2), xlab="Time", ylab="Rate", log="xy")
```
